### 2018-05-22 FrascatiPlot/Paper/NucleiB2.tex
Minor updates to text

The coefficients, $a = 0.339$ and $b = 0.128$, have been determined by fitting linearly the ALICE data, and the parameterisation is reported in Fig. \ref{fig:radiiparam}. These values are consistent with the radius from kaon femtoscopy for $m_{\mathrm{T}} \approx 1$ \GeVc~in low-multiplicity pp collisions \cite{Abelev:2012sq} and the radius from pion femtoscopy in high-multiplicity \PbPb~collisions at the highest available $k_{\mathrm{T}} \approx 0.8$ \GeVc~\cite{Adam:2015vna}. The highest $k_{\mathrm{T}}$ bin was chosen as it corresponds in $m_{\mathrm{T}}$ to the lowest transverse momentum per nucleon (\pt/$A \approx 0.8$ \GeVc) accessible by ALICE for the measurement of nuclei production. 
Ideally, one would use the proton femtoscopic radii for such study, but given that these measurements are not  available in all systems, we assume that $m_{\mathrm{T}}$-scaling holds for HBT radii \cite{Adam:2015vja}.

@@

\section{Statistical-thermal approach and blast-wave}\label{sec:thermal}
\section{Comparison with experimental data}\label{sec:comparison}
- excess binding energy needs to be released to the system to make coalescence work

>>>>

The coefficients, $a = 0.339$ and $b = 0.128$, have been determined by fitting linearly the ALICE data, and the parameterisation is reported in Fig. \ref{fig:radiiparam}. 
These values are consistent with the radius from kaon femtoscopy for $m_{\mathrm{T}} \approx 1$ \GeVc~in low-multiplicity pp collisions \cite{Abelev:2012sq} and the radius from pion femtoscopy in high-multiplicity \PbPb~collisions at the highest available $k_{\mathrm{T}} \approx 0.8$ \GeVc~\cite{Adam:2015vna}. 
The highest $k_{\mathrm{T}}$ bin was chosen as it corresponds in $m_{\mathrm{T}}$ to the lowest transverse momentum per nucleon (\pt/$A \approx 0.8$ \GeVc) accessible by ALICE for the measurement of nuclei production. 
Ideally, one would use the proton femtoscopic radii for such study, but given that these measurements are not  available in all collision systems, we assume that $m_{\mathrm{T}}$-scaling holds for HBT radii \cite{Adam:2015vja}.

@@

\section{Statistical-thermal approach and blast-wave}\label{sec:thermal}

Nuclei form at chemical freeze-out and their yields are determined only by mass and chemical freeze-out temperature:  dN/dy ~ exp (-m/Tch)
pT spectra have been modeled with a Blast-Wave parameterization, with params. fixed by fit to ?,K,p

Normalisation for the spectra is fixed to the d/? (3He/?) ratio from thermal model times the measured ? yield.

Normalisation for 3LH is extracted from the 3He and the S3 predicted by thermal model

\section{Comparison with experimental data}\label{sec:comparison}
- excess binding energy needs to be released to the system to make coalescence work
